To be FAIR: Theory Specification Needs an Update

### 2025-06-08 action_letter.Rmd
update 2025-06-08 09:35:02.868689

Not sure what to do with this! I'm not 100% convinced that the disciplinary differences as the Reviewer describes exist, and I personally do not take a values based approach - I am more interested in "how to" improve social scientific research, and once I know the answer, I am intrinsically motivated to adopt that procedure. I guess I believe that most scholars are doing what they think is best given what they know, and I think that by exposing them to new and better ideas, they will change their ways. I don't see a need to moralize.

>>>>

We appreciate this thoughtful and provocative comment, which explores the broader sociological and cultural dimensions of scientific reform.
We are sympathetic to the reviewer’s view that the challenges facing psychology are not solely technical or procedural, but likely also reflect deeper issues of norms and values.

That said, we are not sure that we are best positioned to engage with these issues, nor that the present paper would be the best place for such an argument.
As methodologists, our primary aim in this paper is to articulate what FAIR theory affords: a framework that supports better theory specification, sharing, and reuse.
We believe this contribution is most effective when kept sharply focused on the practical infrastructure and its scientific use cases.

We do not mean to suggest that infrastructure alone is sufficient, nor do we discount the importance of cultivating scientific values.
However, we believe that meta-scientists and sociologists of science would be better positioned to engage with the topics of norms and values,
and that these topics are better suited to empirical enquiry - i.e., establishing what the most widely held norms and values are, and how these relate to endorsements of academic practices.

We are sympathetic to the Reviewer's meta-scientific considerations,
and we hope that the Reviewer will agree that - while there is clearly a need for enquiry into norms and values - the present paper might not be the best avenue for it.
